data preparation

### 2025-04-07 01_data_preparation.Rmd
folder creation

projet_lac_data |> 
  distinct(LakeBasin)
```

@@

```
##Data frames for GAMs
We compiled four data frames for the four types of general additive models that 
were run: Species with 1) binomial dataoccurring in one lake,
2) abundance data occurring in one lake, 3) binomial data 
occuring in multiple lakes, 4) abundance data and occuring in multiple lakes.

>>>>

projet_lac_data |> 
  distinct(LakeBasin)

# create folder needed in the directory

folder_name <- "data_frame_models"
if (!dir.exists(folder_name)){
  dir.create(folder_name)}

@@

```
##Data frames for GAMs
We compiled four data frames for the four types of general additive models that 
were run: Species with 1) binomial data occurring in one lake,
2) abundance data occurring in one lake, 3) binomial data 
occuring in multiple lakes, 4) abundance data and occuring in multiple lakes.
